---
title: "FinalReportQ4"
author: "Blanca Mares"
date: "11/26/2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastl <- filter(avast,LGBTQ=="gay")

```


#  Question 3 (Straight indviduals)

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

In question 3 our goal is to determine how the AID preventive druh should be working with respect to to each straight indvidual.

\(H_0\):There is no difference in the AID preventive drug that is independent to the LGBTQ of the straight indivduals.

\(H_A\):There is a statistical difference between AID preventive drug  and to those independent to the LGBTQ of the straight indivduals. 

## Methods
for this question I will be using the barchart and chisq test and the fisher test to decide if there is a correlection between bein a gay person and if the new AIDS drug works.
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

We will be using both graphical descriptive and numerical descriptive results.

### Descriptive Results



#### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We use bar charts to compare Numerical vs Numerical data.

```{r}
barchartGC(~infected + treatment,data=avastl)
barchartGC(~infected + treatment,data=avastl,type="percent")
```

#### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
table1 <- xtabs(~infected + treatment, data=avastl)
rowPerc(table1)
colPerc(table1)
```
According to these stats most white gun owners are also in favor of the death penalty. Statistically the data states if you own a gun you’re in favor of the death penalty

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
```
Here we get a P-value of 0.0005, we reject the null hypotheses.

# Discussion and Conclusion

Based on all the test and charts that I have done on this the drug is not effective for gay people. More people that took this drug got this disease.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

