---
title: "Aides Drug"
author: "Blanca Mares"
date: "11/19/2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <- filter(avast,sex=="gal")

```


# Introduction

For this test I will be seeing if the new drug for aids is affected based on if you are a female. Are more females getting aides with the drug or not? 
$H_0$ There is no correlation between a person being a female and them havingthe medication work to not get Aids.
$H_A$: If a person is a female thrn the drug will not work for them.


<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods
For this question I will be using the barchart, chiq and the fisher test to show the correlation between being a female and this Aids drug working for you.

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~infected+treatment,data=avastf,type="percent" )
barchartGC(~infected+treatment,data=avastf)
```

Based on the data above there is a smaller persentage of females that got aides while taking the drug, than those that took the placebo. The drug is effective since less females contracted aides that took the drug than those that took the placebo.


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->



### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment,data=avastf)
rowPerc(table1)
colPerc(table1)
```
On this table we can see more accurately that 31.42% of the females who got AIDS took the drug compared to the 68.58% who took placebo.

This table also shows that 4.35% of the females who took the drug got AIDS compared to the 9.16% of the females who took placebo and got the disease.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->




## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
```

A total of 678 out of the 9975 females in the study got the disease. Out of those females 213 took the drug and 465 had took the placebo.

Overall, it appears that the drug did not make a significant 

# Discussion and Conclusion

This drug is effective for females. Based on the p-value I reject the null hypothies. It is an effective drug.

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
