---
title: "finalreportQ2"
author: "Blanca Mares"
date: "11/21/2019"
output: html_document
---


```{r}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

## QUESTION 2 (Everyone)

 How do we determine how the drug should be working with respect to the infected and the treatment group?
 
 \(H_0\):There is no difference in the indivduals who are infected to AIDS and to those independent of their subgroup.

\(H_A\):There is a statistical difference between the indivuals who a are infected to AIDS and to those independent to their subgroup


# Methods

We will be using both graphical descriptive and numerical descriptive results.

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


```{r}
barchartGC(~infected + treatment,data=avast)
barchartGC(~infected + treatment,data=avast,type="percent")
```
  The barchart is stating that 40% of people taking the AID's preventive drug have AIDS and 58% of the people taking the placebo are infected with AIDS. The subgroups that are taking the AIDS preventive drug/placebo are men, women, straight, gay, and DrugUsers.There is only a 18% difference because those taking the drug and placebo.  

```AIDS PREVENTIVE DRUG
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment , data=avast)
rowPerc(table1)
colPerc(table1)
```
Basically the table is stating that of the indviduals that take the AID's preventive drug and placebo are 50/50 based on the data. There is barely a satistical difference betttween those who are taking the AIDS preventive drug ans those who are taking the placebo.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
```
Based on the satistics for those taking the AID preventive drug is 13.06 and the placebo is 12.40. There is no satistical difference. 
The p-value is 0, we reject the null hypothesis. 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based on the chisq test 423 who took the drug got AIDS and 612 that took the placebo got AIDS. So over all for all the people this drug worked for the most part. It helped people to not  contracted AIDS.



